---
title: "South Sudan Lymphatic Filariasis Progress Report 2014-2024"
author: "Emalee Martin"
date: "`r Sys.Date()`"
output: html_document
---
```{r, setup, echo = FALSE, warning = FALSE, message = FALSE }
library(dplyr)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, here-i-am, include = FALSE}
here::i_am(
  "South-Sudan-LF-Progress-Report.Rmd"
)
```

```{r, load-data}
clean_data <- readRDS(here::here("output/clean_data.rds"))
```
## Introduction
The purpose of this report is to summarize South Sudan's progress toward eliminating Lymphatic Filariasis (LF). Data were obtained from the ESPEN portal (https://espen.afro.who.int/maps-data/countries/south-sudan#lf--data), which is updated annually by the World Health Organization.

This report focuses on visualizing elimination progress over time. Sudan is composed of `r n_distinct(clean_data$iuCode)` Implementation Units (IUs). The table below summarizes the endemicity status of all IUs from 2014 to 2024.

```{r, table}
table <-readRDS(
  file = here::here("output/table.rds")
)
table
```

The following bar chart illustrates elimination progress among South Sudan's LF endemic IUs.

```{r, graph}
graph <-readRDS(
  file = here::here("output/graph.rds")
)
graph
```

